Weakly informative observations: identifying the weakest player

### 2019-11-19 inst/loser.Rmd
work on issue #22

```{r}
(ans_unconstrained <- maxplist(L,give=TRUE))
```

@@

```{r}
small <- 1e-2  # numerical necessity
ans_constrained <-
maxplist(L,startp=c(small*2,rep(small,n-2)),fcm=rbind(c(1,-1,rep(0,n-3))),fcv=0,give=TRUE)
ans_constrained
```

>>>>

```{r}
(ans_unconstrained <- maxp(L,give=TRUE))
```

@@

```{r}
small <- 1e-2  # numerical necessity
ans_constrained <-
maxp(L,startp=c(small*2,rep(small,n-2)),fcm=rbind(c(1,-1,rep(0,n-3))),fcv=0,give=TRUE)
ans_constrained
```
